Multi-wavelength Radio Continuum Emission Studies of Dust-free Red Giants

### 2013-05-10 draft_07/draft.tex
Added vladamir comment

Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind and low mass-loss rate. Our lack of a Ku-band measurement means that we can only compare the previous 3 cm detection reported in \cite{2007ApJ...655..946W} to ours. We find that there is no significant difference between the two. Interestingly, \cite{2007ApJ...655..946W} report a non-detection of $\alpha$ Tau at 6 cm and placed a 3$\sigma$ upper limit of 0.07 mJy on its emission. In stark contrast to this, we were able to detect the star at 6 cm with a flux density over two times greater than this value. This hint of variability at long wavelengths can only again be confirmed with future high S/N observations.

>>>>

Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind and low mass-loss rate. Our lack of a Ku-band measurement means that we can only compare the previous 3 cm detection reported in \cite{2007ApJ...655..946W} to ours. We find that there is no significant difference between the two. Interestingly, \cite{2007ApJ...655..946W} report a non-detection of $\alpha$ Tau at 6 cm and placed a 3$\sigma$ upper limit of 0.07 mJy on its emission. In stark contrast to this, we were able to detect the star at 6 cm with a flux density over two times greater than this value. This hint of variability at long wavelengths would be in agreement with the broadband nonlinear Alfv\'{e}n wave model of \cite{2010ApJ...723.1210A} but can only be confirmed with future high S/N observations.
